From Freebase to Wikidata: The Great Migration

### 2015-10-15 paper.tex
small changes in abstract

\begin{abstract}
Collaborative knowledge bases that make their data available in machine-readable form
as structured data are central to many companies' data strategies.
One such collaborative knowledge base is Freebase (\url{www.freebase.com}),
initially created with proprietary technologies by a~company called Metaweb,
which was then acquired by Google in 2010.
Another example is Wikidata (\url{www.wikidata.org}),
a~collaborative knowledge base developed in the open since 2012 by Wikimedia Deutschland
and operated by the Wikimedia Foundation.
Due to the success of Wikidata, in~2015, Google decided to shut down Freebase and
help the community with the transfer of its content to Wikidata through a~crowdsourcing approach.
In this paper, we describe the ongoing transfer efforts and data mapping challenges,
and provide an analysis of the process so far.
For the task, we have created a~software solution called \emph{Primary Sources Tool}
that we have released as open source to facilitate this and future data migrations.
Throughout the migration, we have gained deep insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases. 
\end{abstract}

>>>>

\begin{abstract}
Collaborative knowledge bases that make their data freely available in a machine-readable form
are central for the data strategy of many projects and organizations.
One such collaborative knowledge base is Freebase,
initially launched by Metaweb in 2007.
Metaweb was acquired by Google in 2010.
Another example is Wikidata,
a~collaborative knowledge base developed by Wikimedia Deutschland since 2012
and operated by the Wikimedia Foundation.
Due to the success of Wikidata, Google decided 2015 to shut down Freebase and
help the community with the transfer of Freebase's content to Wikidata.
In this paper, we describe the ongoing transfer efforts and data mapping challenges,
and provide an analysis of the effort so far.
We have created the \emph{Primary Sources Tool}
that we have released as open source to facilitate the transfer of this dataset,
but also future data migrations.
Throughout the migration, we have gained insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases. 
\end{abstract}
